---
output: github_document
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-", 
  message = FALSE
)
```

# Central Bank Transparency Data

This package contains the dataset on central bank transparency from
[Dincer and Eichengreen (2014)](http://eml.berkeley.edu/~eichengr/data.shtml).

The maintainer of this package is unaffiliated with those authors, so if you 
use the data please cite it accordingly:

> Dincer and Eichengreen, "Central Bank Transparency and Independence: Updates and
> New Measures", International Journal of Central Banking, Vol. 10, No. 1:
> 189-259, March 2014.

# Installation and example usage

To install the package from Github:

```{r install, eval=FALSE}
devtools::install_github("expersso/cbtransparency")
```

```{r usage, fig.width=5, fig.height=4}
library(cbtransparency)
library(dplyr)
library(ggplot2)

head(transp)

countries <- c("EA", "US", "GB", "SE", "AU", "NZ", "CA")

df_plot <- transp %>%
  filter(measure == "Augmented Transparency by Region") %>%
  filter(iso2c %in% countries) %>% 
  mutate(value = value + runif(length(value), 0.1, 0.2))

ggplot(df_plot, aes(x = year, y = value, color = iso2c)) +
  geom_line() +
  geom_point() +
  theme_bw() +
  labs(x = NULL, y = NULL, color = NULL,
       title = "Central Bank Transparency", 
       subtitle = "Index (greater value = more transparent central bank)",
       caption = "Source: Dincer & Eichengreen (2014)")
```

